Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-11-16 paper/ifo-complexAudio.tex
minor changes, commented out footmisc

An updated schematic is shown in Fig.~\ref{fig:ifo_schematic_podo} and a photograph of the entire optical microphone in Fig.~\ref{fig:setup_pic2}.
See Appendix~\ref{app:circuit_diagram} for a diagram and photograph of the circuit.

@@

\begin{figure*}
	\begin{center}
    %% trim order is <left> <lower> <right> <upper>
	\includegraphics[width=\textwidth,trim={1cm 4.5cm 0.4cm 3.5cm},clip]{figures/notch_and_wiener_superplot_v2.pdf}
	\end{center}
	\caption{\label{fig:BackgroundNotchWienerCombined}
	Time series (left column) and frequency spectrum (right column) results for the background subtraction, notch, and Wiener filters.
	The first and second rows show the original speech recording and raw output from the optical microphone respectively. 
    The third row shows a background noise recording from the optical microphone when no audio signal is played. 
    The fourth row shows the result of subtracting the background noise spectrum in the third row from the recording in the second row. 
	%The second row shows the raw output from the optical microphone.
	%The third row shows the naive technique of subtracting off the noise spectrum from the recorded spectrum.
	The fifth, sixth, and seventh rows show the results of applying the notch filter, the Wiener filter, and both combined, respectively.
	}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/combined_timeseries_melatos.pdf}
	\caption{Time series of an adult male voice (saying ``A cathode ...'') showing the source (top panel), the optical microphone recording (middle panel), and the recording after filtering with the logMMSE estimator (bottom panel). One second of the one minute recording is shown. The rise at the start of the bottom panel is expected when filtering a signal of finite duration.}
	\label{fig:logMMSE_timeseries}
\end{figure*}

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/combined_spectrum_melatos.pdf}
	\caption{Spectrum of optical microphone recording of the same adult male voice in Fig.~\ref{fig:logMMSE_timeseries} showing the source (top panel), the optical microphone recording (middle panel), and the recording after filtering with the logMMSE estimator (bottom panel). The spectrum shows only a detail of the total frequency domain (there is little activity at higher frequencies) and has truncated peaks at amplitude 2 which otherwise dominate the plot.}
	\label{fig:logMMSE_spectrum}
\end{figure*}

>>>>

An updated schematic and a photograph of the entire optical microphone are shown in the left and right panels of Fig.~\ref{fig:ifo_schematic_podo}, respectively.
See Appendix~\ref{app:circuit_diagram} for a diagram and photograph of the circuit.

@@

\begin{figure*}
	\begin{center}
    %% trim order is <left> <lower> <right> <upper>
    % height=0.5\textheight,trim={1cm 4.5cm 0.4cm 3.5cm},clip
	\includegraphics[height=0.85\textheight]{figures/notch_and_wiener_superplot_v2.pdf}
	\end{center}
	\caption{\label{fig:BackgroundNotchWienerCombined}
	Time series (left column) and frequency spectrum (right column) results for the background subtraction, notch, and Wiener filters.
	The first and second rows show the original speech recording and raw output from the optical microphone respectively. 
    The third row shows a background noise recording from the optical microphone when no audio signal is played. 
    The fourth row shows the result of subtracting the background noise spectrum in the third row from the recording in the second row. 
	%The second row shows the raw output from the optical microphone.
	%The third row shows the naive technique of subtracting off the noise spectrum from the recorded spectrum.
	The fifth, sixth, and seventh rows show the results of applying the notch filter, the Wiener filter, and both combined, respectively.
	}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=0.8\textwidth]{figures/combined_timeseries_melatos.pdf}
	\caption{Time series of an adult male voice (saying ``A cathode ...'') showing the source (top panel), the optical microphone recording (middle panel), and the recording after filtering with the logMMSE estimator (bottom panel). One second of the one minute recording is shown. The rise at the start of the bottom panel is expected when filtering a signal of finite duration.}
	\label{fig:logMMSE_timeseries}
\end{figure*}

\begin{figure*}
	\includegraphics[width=0.8\textwidth]{figures/combined_spectrum_melatos.pdf}
	\caption{Spectrum of optical microphone recording of the same adult male voice in Fig.~\ref{fig:logMMSE_timeseries} showing the source (top panel), the optical microphone recording (middle panel), and the recording after filtering with the logMMSE estimator (bottom panel). The spectrum shows only a detail of the total frequency domain (there is little activity at higher frequencies) and has truncated peaks at amplitude 2 which otherwise dominate the plot.}
	\label{fig:logMMSE_spectrum}
\end{figure*}

### 2020-11-16 paper/paper_main.tex
minor changes, commented out footmisc

% GravExplain
%\documentclass[prb,reprint,nofootinbib]{revtex4-1} 
\documentclass[pra,superscriptaddress,reprint,amsmath,amssymb,nofootinbib]{revtex4-1}
% \documentclass[prb,preprint,letterpaper,noeprint,longbibliography,nodoi,footinbib]{revtex4-1}

% Note that AJP uses the same style as Phys. Rev. B (prb).
% The AIP Style Manual\cite{AIPstylemanual} is an indispensable reference on good physics writing, covering everything from planning and organization to standard spellings and abbreviations.
% Most important of all, please familiarize yourself with the AJP Statement of Editorial Policy,\cite{editorsite} which describes the types of manuscripts that AJP publishes and the audience for which AJP authors are expected to write.
% We look forward to receiving your submission to AJP.
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{float}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref}
% \usepackage{siunitx}
\usepackage{textcomp}
\usepackage{subfiles}
\usepackage[bottom]{footmisc}
\usepackage{comment}
\usepackage{algpseudocode}
% \usepackage{algorithm}
% \usepackage{algorithmic}

@@

\begin{acknowledgments}
The authors are grateful to Jude Prezens, Alex Tolotchkoc, and Blake Molyneux for their technical advice and generous assistance; Patrick Meyers, Margaret Millhouse, Sofia Suvorova for useful discussions; Patrick Clearwater, Patrick Meyers, Suk Yee Yong, Lucy Strang, Julian Carlin, Sanjaykumar Patil, and Alex Cameron for early work on the interferometer design requirements and construction; and the LIGO Education Public Outreach working group, in particular Anna Green, Lynn Cominsky and Sam Cooper for their helpful feedback and suggestions.  
This research is supported by the Australian Research Council Centre of Excellence for Gravitational Wave Discovery (OzGrav) (project number CE170100004). 
Financial support towards hardware was provided by the Institute of Physics International Member Grant and the OzGrav Outreach Support scheme. 
Travel support was provided by the Australian National PhB Science program.
This work has been assigned LIGO document number P2000386.

>>>>

% GravExplain
%\documentclass[prb,reprint,nofootinbib]{revtex4-1} 
\documentclass[aps,pra,superscriptaddress,reprint,nofootinbib]{revtex4-1}
% \documentclass[prb,preprint,letterpaper,noeprint,longbibliography,nodoi,footinbib]{revtex4-1}

% Note that AJP uses the same style as Phys. Rev. B (prb).
% The AIP Style Manual\cite{AIPstylemanual} is an indispensable reference on good physics writing, covering everything from planning and organization to standard spellings and abbreviations.
% Most important of all, please familiarize yourself with the AJP Statement of Editorial Policy,\cite{editorsite} which describes the types of manuscripts that AJP publishes and the audience for which AJP authors are expected to write.
% We look forward to receiving your submission to AJP.
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{float}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref}
% \usepackage{siunitx}
\usepackage{textcomp}
\usepackage{subfiles}
% \usepackage[bottom]{footmisc}
\usepackage{comment}
\usepackage{algpseudocode}
% \usepackage{algorithm}
% \usepackage{algorithmic}
\usepackage{lmodern}

\usepackage{silence}
\WarningFilter{revtex4-1}{Repair the float}

@@

\begin{acknowledgments}
The authors are grateful to Jude Prezens, Alex Tolotchkoc, and Blake Molyneux for their technical advice and generous assistance; Patrick Meyers, Margaret Millhouse, Sofia Suvorova for useful discussions; Patrick Clearwater, Patrick Meyers, Suk Yee Yong, Lucy Strang, Julian Carlin, Sanjaykumar Patil, and Alex Cameron for early work on the interferometer design requirements and construction; and the LIGO Education Public Outreach working group, in particular Anna Green, Lynn Cominsky and Sam Cooper for their helpful feedback and suggestions.  
This research is supported by the Australian Research Council Centre of Excellence for Gravitational Wave Discovery (OzGrav) (project number CE170100004). 
Financial support towards hardware was provided by the Institute of Physics International Member Grant and the OzGrav Outreach Support scheme. 
Travel support was provided by the Australian National University PhB Science program.
This work has been assigned LIGO document number P2000386.
